Supplementary information

### 2018-06-18 supplementary_information.Rmd
Add data range analysis and some more review responses

```{r libraries, include = FALSE}
library(knitr)
library(kableExtra)
library(drake)
library(ggplot2)
```

@@

```{r pairwise_correlation_table, echo = FALSE, results = "asis"}
corr_results <- readd(corr_processed)
kable(
  corr_results %>%
    dplyr::select(pft, yvar, xvar, corr_value, present, missing),
  "latex",
  booktabs = TRUE, longtable = TRUE, escape = FALSE,
  col.names = c("PFT", "Trait 1", "Trait 2", "Correlation (95\\% CI)", "present", "missing"),
  caption = "Pairwise trait correlation values for each plant functional type. Values with asterisks indicate correlations significantly different from zero ($p < 0.05$)."
)

correlation_scatter_cap <- paste(
  "Pairwise mean squared trait correlation values as a function of sample size.",
  "Note that the x-axis uses a $\\log_10$ scale."
)
correlation_fig_cap <- paste(
  "Fraction of statistically significant ($p < 0.05$) pairwise trait correlation estimates",
  "as a function of sample size for each plant functional type."
)
```

@@

```{r correlation_sample_size_analysis, echo = FALSE, fig.cap = correlation_fig_cap}
corr_binned <- corr_results %>%
  dplyr::mutate(
    ss_bin = cut(
      present,
      c(0, 1, 10, 25, 50, 100, 500, 1000, Inf),
      c("0", "< 10", "< 25", "< 50", "< 100", "< 500", "< 1000", "> 1000"),
      include.lowest = TRUE,
      right = FALSE
    )
  ) %>%
  group_by(pft, ss_bin) %>%
  summarize(frac_significant = mean(significant))

@@

>>>>

```{r libraries, include = FALSE}
library(knitr)
library(kableExtra)
library(drake)
library(ggplot2)

correlation_scatter_cap <- paste(
  "Pairwise mean squared trait correlation values as a function of sample size.",
  "Note that the x-axis uses a $\\log_{10}$ scale."
)

correlation_fig_cap <- paste(
  "Fraction of statistically significant ($p < 0.05$) pairwise trait correlation estimates",
  "as a function of sample size for each plant functional type."
)

correlation_range_cap <- paste(
  "Relationship between pairwise correlation strength and data range for each PFT.",
  "In each pair of sub-panels, the left panel is relationship between pairwise correlation",
  "and the range of the variable on the x axis",
  "while the right panel is the relationship between pairwise correlation",
  "and the y variable",
  "(For instance, in the two-panel figure in row 1 column 2,",
  "the left panel is the SLA-leaf lifespan correlation as a function of the range of SLA",
  "and the right panel is the same correlation as a function of the range of leaf lifespan).",
  "Data range is expressed as the difference between the 2.5% and 97.5% quantiles of each normalized trait (i.e. $\\frac{X}{E[X]}$).",
  "Grey shading is the 95% confidence interval around a local regression (LOESS).",
  "Upper triangle is area-normalized values, and lower triangle is mass-normalized values."
)
```

```{r mean_value_table, echo = FALSE, results = "asis"}
vals <- readd()
```

@@

```{r pairwise_correlation_table, echo = FALSE, results = "asis"}
corr_results <- readd(corr_processed)
kable(
  corr_results %>%
    dplyr::select(pft, yvar, xvar, corr_value, present, missing),
  "latex",
  booktabs = TRUE, longtable = TRUE, escape = FALSE,
  col.names = c("PFT", "Trait 1", "Trait 2", "Correlation (95\\% CI)", "present", "missing"),
  caption = "Pairwise trait correlation values for each plant functional type. Values with asterisks indicate correlations significantly different from zero ($p < 0.05$)."
)
```

@@

```{r correlation_sample_size_analysis, echo = FALSE, include = FALSE, eval = FALSE, fig.cap = correlation_fig_cap}
corr_binned <- corr_results %>%
  dplyr::mutate(
    ss_bin = cut(
      present,
      c(0, 1, 10, 25, 50, 100, 500, 1000, Inf),
      c("0", "< 10", "< 25", "< 50", "< 100", "< 500", "< 1000", "> 1000"),
      include.lowest = TRUE,
      right = FALSE
    )
  ) %>%
  group_by(pft, ss_bin) %>%
  summarize(frac_significant = mean(significant))

@@

```{r correlation_range_analysis, echo = FALSE, results = "hide", warning = FALSE, fig.cap = correlation_range_cap, fig.dim = c(12, 12)}
readd(corr_range_plot_gg)
```
